Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-08 manuscript.tex
Discussion
Update on Overleaf.

However, it was not until the study of the interaural time difference (ITD) by Gerstner in 1996~\citep{gerstner_neuronal_1996} that it was discovered that this delay is not homogeneous for all neurons of the same type and species, but adapts according to their function. This ITD is a biological mechanism which allows for the azimutal localization of sound by barn owls, by organically computing the difference in arrival time of a sound between their two ears. According to \citep{gerstner_neuronal_1996}, there is a true paradox in auditory neural systems since “neural networks encode behaviourally relevant signals in the range of a few $\mu s$ with neurons that are at least one order of magnitude slower”, therefore necessarily need to play on the response time to do so. \citet{pena_2001} conducted an extended study on ITD in order to confirm this theory by identifying the coincidence detector involved, which the authors situated in the nuclear laminaris. A first hypothesis suggested that the sound coincidence was detected using stereausis, i.e. the temporal disparity between left and right cochlear loci in the owl's brain. However it was quickly set aside as the predictions did not match the measured disparities in the loci, and no variations were perceived in the nuclear laminaris for a similar sound intensity in both owl ears. The authors support a second hypothesis, that of different axonal delays in the ipsi and contralateral cochlear nucleus magnocellularis. \citet{seidl_mechanisms_2010} experimentally seconds this hypothesis of a "coarse" regulation of delay, as the authors conclude that regulations at different sites within individual axons of at least two parameters, namely the axon diameter and internode distances, might be responsible for precise adjustments of physiological delays thus allowing the ITD detection. These experiments also confirmed previous studies stating that the conduction velocity of a spike in a neuron (in other words, its delay) depends strongly on the axon diameter \cite{gasser_1939} and the internode distance between Ranvier nodes \cite{brills_1977} --- instead of the axon's length as was previously thought.

@@

In that perspective, it is
essential that such models
are tested on ecologically-
relevant, real-world scenarios.
Indeed, classic convolutional
neural networks emerged
as optimal solutions for
instance he classify static
images into categories, yet
thay are not well adapted
for processing dynamic,
multimodal sensory flows.
The emerging necessity to be
able to process more complex
flows, such as the multiples
flows of information in a
car designed for autonomous
driving, necessitates to
modify modelling paradigms.
and in particular to take into
account that the generated actions
may modify the sensory inputs.
Notably, the protocols used
as well in neurobiology,
theory on engineering should
take into account this hovel
complexity.
Ultimately, the community should
encourage the adoption of open,
reproducible science. Indeed,
the different models that we have
displayed often come with the
tools necessary he reproduce the
results obtained. This is true
in neurobiology (Belles), in
theoretical neuroscience (Ishi)
or in engineering (PAMI).
This aspect is essential to
foster the emergence of inter-
disciplinary projects, such
as model-driven neurobiological
experiments or biologically-
inspired vennomorphic
engineering.
As such, this review aimed
at paving the way to openly
share the variety of
resources and to offer an
unified view on the role of
precise spiking motifs in
neuroscience.

>>>>

However, it was not until the study of the interaural time difference (ITD) by~\citet{gerstner_neuronal_1996} that it was discovered that this delay is not homogeneous for all neurons of the same type and species, but adapts according to their function. This ITD is a biological mechanism which allows for the azimutal localization of sound by barn owls, by organically computing the difference in arrival time of a sound between their two ears. According to \citep{gerstner_neuronal_1996}, there is a true paradox in auditory neural systems since “neural networks encode behaviourally relevant signals in the range of a few $\mu s$ with neurons that are at least one order of magnitude slower”, therefore necessarily need to play on the response time to do so. \citet{pena_2001} conducted an extended study on ITD in order to confirm this theory by identifying the coincidence detector involved, which the authors situated in the nuclear laminaris. A first hypothesis suggested that the sound coincidence was detected using stereausis, i.e. the temporal disparity between left and right cochlear loci in the owl's brain. However it was quickly set aside as the predictions did not match the measured disparities in the loci, and no variations were perceived in the nuclear laminaris for a similar sound intensity in both owl ears. The authors support a second hypothesis, that of different axonal delays in the ipsi and contralateral cochlear nucleus magnocellularis. \citet{seidl_mechanisms_2010} experimentally seconds this hypothesis of a "coarse" regulation of delay, as the authors conclude that regulations at different sites within individual axons of at least two parameters, namely the axon diameter and internode distances, might be responsible for precise adjustments of physiological delays thus allowing the ITD detection. These experiments also confirmed previous studies stating that the conduction velocity of a spike in a neuron (in other words, its delay) depends strongly on the axon diameter \cite{gasser_1939} and the internode distance between Ranvier nodes \cite{brills_1977} --- instead of the axon's length as was previously thought.

@@

In that perspective, it is essential that such models are tested on ecologically- relevant, real-world scenarios. Indeed, classic convolutional neural networks emerged as optimal solutions for instance he classify static images into categories, yet thay are not well adapted for processing dynamic, multimodal sensory flows. The emerging necessity to be able to process more complex flows, such as the multiples flows of information in a car designed for autonomous driving, necessitates to modify modelling paradigms. and in particular to take into account that the generated actions may modify the sensory inputs. Notably, the protocols used as well in neurobiology, theory on engineering should take into account this hovel complexity.

Ultimately, the community should encourage the adoption of open, reproducible science. Indeed, the different models that we have displayed often come with the tools necessary he reproduce the results obtained. This is true in neurobiology (Belles), in theoretical neuroscience (Ishi) or in engineering (PAMI). This aspect is essential to foster the emergence of inter- disciplinary projects, such as model-driven neurobiological experiments or biologically- inspired vennomorphic engineering. As such, this review aimed at paving the way to openly share the variety of resources and to offer an unified view on the role of precise spiking motifs in neuroscience.
